---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(dplyr)
```

# nflfastR-roster

This repo hosts roster data intended to be used with [nflfastR](https://mrcaseb.github.io/nflfastR/).

The data is a combination of 

* the legacy roster data from the [nflfastR data repo](https://github.com/guga31bb/nflfastR-data/tree/master/roster-data) (for the seasons 1999 to 2019) and

* weekly scraped rosters from [nfl.com](https://www.nfl.com/teams/) (beginning with season 2020).

For that reason many variables will show `NA` beginning in 2020.

The nflfastR play-by-play data uses special player IDs (UUIDs version 4). The roster data in this repo joins those IDs to the scraped rosters. Therefore only players who appear as `passer`, `rusher`, or `receiver` in the nflfastR play-by-play data will show the `pbp_id`. This ID can be used to join the roster data to the play-by-play data.

The following table shows an example output of the 2020 data for Patrick Mahomes. The variables `pbp_id` and `pbp_name` are joinable to nflfastR.

```{r, echo=FALSE}
readRDS("data/nflfastr-roster.rds") %>% 
  filter(team.season == 2020, teamPlayers.displayName == "Patrick Mahomes") %>% select(team.season:teamPlayers.displayName, teamPlayers.position, teamPlayers.birthDate, teamPlayers.collegeName:teamPlayers.weight, pbp_id, pbp_name, -teamPlayers.jerseyNumber) %>% 
  knitr::kable()
```

Please note:
This repo updates itself every 15 minutes by joining the most recent [nflfastR play-by-play data](https://github.com/guga31bb/nflfastR-data/tree/master/data) to the scraped rosters. So if a very new player ID is missing please wait until the data repo is updated.
