---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(dplyr)
```

# nflfastR-roster

This repo hosts roster data intended to be used with [nflfastR](https://mrcaseb.github.io/nflfastR/).

We used to combine

* the legacy roster data from the [nflfastR data repo](https://github.com/guga31bb/nflfastR-data/tree/master/roster-data) (for the seasons 1999 to 2019) and

* weekly scraped rosters from [nfl.com](https://www.nfl.com/teams/) (beginning with season 2020).

However, in the meanwhile we were able to decode the special player IDs (UUIDs version 4) in the nflfastR play-by-play data using the new funtion `nflfastR::decode_player_ids()`. Therefore the function `nflfastR::fast_scraper_roster()` returned to [nflfastR](https://mrcaseb.github.io/nflfastR/) providing roster data from the  free to use [Sleeper API](https://docs.sleeper.app/#fetch-all-players).

The following table shows an example output of all 2020 QBs of the Kansas City Chiefs. The variable `gsis_id` can be used to join the data to nflfastR play-by-play data.

```{r, echo=FALSE}
nflfastR::fast_scraper_roster(2020) %>% filter(team == "KC", position == "QB") %>% knitr::kable()
```

Please note:
This repo updates itself every day at 3AM ET.
